---
title: "This time it's personal"
subtitle: "Livecoding a personal R package <br><br><a href='bit.ly/laerug_pkg_cloud'>bit.ly/laerug_pkg_cloud</a><br><br><a href='bit.ly/laerug_pkg_repo'>bit.ly/laerug_pkg_repo</a>"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: middle, center, inverse

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, tibble.max_extra_cols = 6, tibble.width = 60)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.align = "center", dpi = 320)
```

```{r, css_theme, echo=FALSE}
htmltools::includeCSS("https://raw.githubusercontent.com/malcolmbarrett/kakashi/master/kakashi.css")
```

# We're going to make a package *right now*

---

class: middle, center, inverse, 

## **`usethis::create_package("mbmisc2")`**

---

class: middle, center, inverse, 

# **`library(devtools)`**
# **`library(usethis)`**

---

class: middle, center, inverse, 

# **`use_r("labs_wrap")`**

---

class: middle, center, inverse, 

# **`use_package("ggplot2")`**
# **`use_package("tibble")`**
# **`use_package("dplyr")`**
# **`use_package("stringr")`**

---

class: middle, center, inverse, 

# `r emojifont::emoji("hammer")` **Build**
# `r emojifont::emoji("heavy_check_mark")` **R CMD Check**

---

class: middle, center, inverse, 

# **Edit DESCRIPTION**

---

class: middle, center, inverse, 

# **`use_mit_license("Your Name")`**

---

class: middle, center, inverse, 

# **`use_roxygen_md()`**
# **`document()`**

---

class: middle, center, inverse, 

# `r emojifont::emoji("hammer")` **Build**
# `r emojifont::emoji("heavy_check_mark")` **R CMD Check**

---

class: middle, center, inverse, 

# **`use_test("labs_wrap")`**
# **`test()`**

---

class: middle, center, inverse, 

# **`use_git()`**
# **`use_github()`**

---

class: inverse, center

# Resources
## [R Packages, 2nd Edition](https://r-pkgs.org/): The work-in-progress second edition of R Packages. Uses the most cutting edge tools to make your life easier. Free online.
## [R Packages, 1st Edition](http://r-pkgs.had.co.nz/): The first edition of R Packages. Still very good! Free online.
